\cvsection{Experience}

\begin{cventries}
  \cventry
    {\textbf{Data Scientist - Homeowner Insurance} | Outstanding Performance Evaluation} % Job title
    {Data Lab - Intact Insurance} % Organization
    {Toronto, Canada} % Location
    {Sept 2020 - Dec 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {\descriptionstyleboldcolor{Project:} Predict the Loss Cost of a Policy Holder using \descriptionstylebold{Machine Learning}}
        \item {Improved Model Training/Evaluation run-time by \descriptionstylebold{30\%} and memory efficiency by implementing cached feature matrices}
        \item {Overhauled the implementation of various mission critical model evaluation visualisations and improved the run-time by \descriptionstylebold{300x}, saving \descriptionstylebold{12 hours/week} for multiple teams (8+)}
        \item {Developed a new Model Evaluation Pipeline using Bash, Python and internal libraries to save \descriptionstylebold{1.5 weeks} of run-time and \descriptionstylebold{3 days of developer time} per month}
        \item {Developed Model Visualisation Customisation tools to allow users to create better charts much more easily!}
        \item {Managed a Masters Student Data Science Intern throughout the project and doubled their workflow efficiency!}
      \end{cvitems}
    }

  \cventry
    {\textbf{Data Scientist - Credit Cards} | Outstanding Performance Evaluation} % Job title
    {TD Bank} % Organization
    {Toronto, Canada} % Location
    {Jan. 2020 - May 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {\descriptionstyleboldcolor{Project}: Identify credit card customers fit for a more premium credit card and find way to sell the product using \descriptionstylebold{Machine Learning}}
        \item {Independently built the \descriptionstylebold{Multi-Class Classification} Model Using \descriptionstylebold{XGBoost}, \descriptionstylebold{HyperOpt} for \descriptionstylebold{Hyper Parameter Tuning} and, \descriptionstylebold{SHAP} for feature importance, all done in \descriptionstylebold{Python}}
        \item {Rebuilt the \descriptionstylebold{Feature Engineering} from scratch, decreasing the run-time by \descriptionstylebold{200x} while making the code base more modular and accessible to future developers.}
        \item {The project is evaluated to generate \descriptionstylebold{$\sim$ 50 MM CAD} over then next 5 years}
        \item {Overhauled Employee Credit Cards products leading in \descriptionstylebold{$9$ MM CAD} in Annual Profit and improve the user acquisition by \descriptionstylebold{35$\%$}}
      \end{cvitems}
    }

  \cventry
    {\textbf{Data Scientist - Commercial Banking} | Outstanding Performance Evaluation} % Job title
    {Scotiabank} % Organization
    {Toronto, Canada} % Location
    {Sept. 2019 - Jan. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {\descriptionstyleboldcolor{Project}: Re-Launch a new Django Web App to recommend Scotiabank Customer Relationship Managers the best product to sell to their Commercial Clients.}
        \item {Built an \descriptionstylebold{NLP (LDA)} model to analyse user feedback and identify the main reasons for user dislike some recommendations. This allowed us to improve the Web App User Experience as well as the ML models.}
        \item {Strategized and built the main new feature to explain product recommendations made by the \descriptionstylebold{XGBoost} model using \descriptionstylebold{SHAP}}
        \item {Proposed and built a new feature in the Django App to help Scotiabank reach out to and support Women Lead Businesses to improve equal opportunity, using \descriptionstylebold{Django, PostGreSQL, JavaScript \& AJAX}.}
      \end{cvitems}
    }

  \cventry
    {\textbf{Data Analyst / Full Stack Developer} | Outstanding Performance Evaluation} % Job title
    {Center for Pattern Analysis and Machine Intelligence at UWaterloo AI} % Organization
    {Waterloo, Canada} % Location
    {Jan. 2019 - Apr. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {\descriptionstyleboldcolor{Project}: Develop a 2-3 week Forecast for the price of Fresh Produce for Loblaws.}
        \item {Independently built a \descriptionstylebold{Dockerized Flask Web App} to help researchers easily access, manage and analyse datasets stored on Azure Cloud. This App saved research group \descriptionstylebold{8k CAD annually} and provided quick and easy way to access the data!}
        \item {Developed Python Scripts to Automate Data Transformations, Analysis and Cleaning using Pandas and Numpy from legacy Excel Manual Work, saving \descriptionstylebold{5 hours/week} of researchers time.}
        \item {Managed an intern to help push the app in production.}
		\item {Built an \descriptionstylebold{ARIMA time series model} to predict future procurement prices of fresh produce for a Loblaw’s Project using \descriptionstylebold{Python and MATLAB}}
      \end{cvitems}
    }
\end{cventries}
